Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-06-03 ms.tex
while editing S5.2...
changed a few () to [] for functions
all f_c -> f_cyc

First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age. 
Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
%%%%%%%%%% 
\begin{eqnarray}
B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
f_c &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
\end{eqnarray}
%%%%%%%%%%
under this model.

@@

Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%% 
%\memoYF{cite original paper!}. 
Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them. 
Note that, within this framework, the {\it spectral} radio flux has  necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}.

@@

%
At the magnetic stand-off point, 
%%%
\begin{equation}
m_p n(r_s) v^2 = \frac{B(r_s)^2}{2\pi }
\end{equation}
%%%
and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
%%%
\begin{equation}
\frac{mv^2}{2} \propto \frac{1}{r}
\end{equation}
%%%
while magnetic pressures increases (by beaming?) by 
%%%
\begin{equation}
\frac{B^2}{8\pi } \propto \frac{1}{r^6}
\end{equation}
%%%
therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.

@@

where $B_s$ is the magnetic field at the magnetic stand-off point. 
Because $v_{\bot }^2 < v^2$, 
%%%
\begin{equation}
\left. \frac{B_c}{B}\right|_{r=r_s} = \frac{4\pi n(mv_{\bot }^2)}{3 B^2}= \frac{\rho_K}{3\rho_B},
\end{equation}
%%%

%
At the magnetic stand-off point, 
%%%
\begin{equation}
m_p n(r_s) v^2 = \frac{B(r_s)^2}{2\pi }
\end{equation}
%%%
and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
%%%
\begin{equation}
\frac{mv^2}{2} \propto \frac{1}{r}
\end{equation}
%%%
while magnetic pressures increases (by beaming?) by 
%%%
\begin{equation}
\frac{B^2}{8\pi } \propto \frac{1}{r^6}
\end{equation}
%%%
therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.

@@

Note that that for a plasma of protons and electrons in solar wind the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons. \memoYF{necessary to mention?}

>>>>

First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age. 
Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
%%%%%%%%%% 
\begin{eqnarray}
B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
\end{eqnarray}
%%%%%%%%%%
under this model.

@@

Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyc}} \\
&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%% 
%\memoYF{cite original paper!}. 
Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them. 
Note that, within this framework, the {\it spectral} radio flux has  necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}.

@@

%
At the magnetic stand-off point, 
%%%
\begin{equation}
m_p n[r_s] v^2 = \frac{B[r_s]^2}{2\pi }
\end{equation}
%%%
and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
%%%
\begin{equation}
\frac{mv^2}{2} \propto \frac{1}{r}
\end{equation}
%%%
while magnetic pressures increases (by beaming?) by 
%%%
\begin{equation}
\frac{B^2}{8\pi } \propto \frac{1}{r^6}
\end{equation}
%%%
therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.

@@

@@

It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons. \memoYF{necessary to mention?}
